QPLIB: A Library of Quadratic Programming Instances

### 2016-11-26 QPLIB-3.tex
added CUTEst
added a few citations, corrected a few typoes
Update QPLIB-3.tex

\begin{itemize}
 \item {\tt POLIP} \url{http://polip.zib.de/pipformat.php}
 %
 \item {\tt MINLP} \url{http://www.gamsworld.org/minlp/minlplib.htm}
 %
 \item {\tt MacMINLP} \url{https://wiki.mcs.anl.gov/leyffer/index.php/MacMINLP}
 %
 \item {\tt Meszaros} \url{http://www.doc.ic.ac.uk/~im/00README.QP}
 %
 \item {\tt BARON Library} \url{http://www.minlp.com/nlp-and-minlp-test-problems}
 %
 \item {\tt GAMS Library} \url{http://www.gamsworld.org/performance/performlib.htm}
\end{itemize}
%
Other QP instances were found in libraries devoted to specific optimization problems that can be modeled as QP, such as Max-Cut, the Quadratic Assignment Problem, Portfolio Optimization problems and several others; for reason of space we refrain from listing all these sources.

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{7}*{Linear}
          & Binary  & Quadratic &  71 \\
          & \multirow{2}*{Mixed}
                    & Convex    &   5 \\
          &         & Quadratic & 277 \\
%          & \multirow{2}*{Integer}
%                    & Convex    &  15 \\
%          &         & Quadratic &   5 \\
          & \multirow{2}*{General}
                    & Convex    &  22 \\
          &         & Quadratic &   8 \\
%\hline
\\
\multirow{4}*{Convex}
          & Binary  & Linear    &  12 \\
          & \multirow{2}*{Mixed}
                    & Linear    &  37 \\
          &         & Quadratic &   3 \\
          & General & Linear    &   1 \\
%\hline
\\
\multirow{7}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &  29 \\
          &         & Linear    & 180 \\
%          &         & Quadratic &   8 \\
          & \multirow{2}*{Mixed}
                    & Linear    &  12 \\
          &         & Quadratic &   9 \\
          & Integer & Linear    &   2 \\
          & \multirow{2}*{General}
                    & Linear    &   1 \\
          &         & Quadratic &   2 \\
\hline
Total     &         &           & 600 \\
%
\bottomrule
\end{tabular}
\label{tab:FinalSet-D}
\caption{Classification of the final set of discrete instances}
\end{table}

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &  14 \\
                         & Quadratic &  71 \\
\multirow{3}*{Convex}    & None      &   6 \\
                         & Box       &   6 \\
                         & Linear    &  50 \\
                         & Convex    &   3 \\
                         & Quadratic &   6 \\
\multirow{3}*{Quadratic} & Box       &   8 \\
                         & Linear    &  19 \\
                         & Convex    &  27 \\
                         & Quadratic &  40 \\
\hline
Total                    &           & 250 \\
%
\bottomrule
\end{tabular}
\label{tab:FinalSet-C}
\caption{Classification of the final set of continuous instances}
\end{table}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Instance Format}\label{subsec:format}
\framebox{TASK X : write }
In the call for instances no specific formats were imposed
%we did not impose a specific format
for the submissions.
%In this phase we also eliminated multiples copies of the same instance.
To evaluate the instances we decided, for practical reasons, to use Gams as common platform for all the experiments involving commercial solvers.
For this reason, we decided to translate all instances into the \texttt{.gms} Gams format.
 In a preliminary phase, all the instances received were divided according to their format and subsequently translated.
In Sect.
%~\ref{subsec:CP_convex}
the tools used
to translate an instance from a given format to the \texttt{.gms} format
%to translate an instance from and to a given format to the \texttt{.gms} format
are described more in detail.\\

>>>>

\begin{itemize}
 \item {\tt BARON Library} \url{http://www.minlp.com/nlp-and-minlp-test-problems}
 %
 \item {\tt CUTEst Library} \url{https://ccpforge.cse.rl.ac.uk/gf/project/cutest/wiki}
 %
 \item {\tt GAMS Library} \url{http://www.gamsworld.org/performance/performlib.htm}
 %
 \item {\tt MacMINLP} \url{https://wiki.mcs.anl.gov/leyffer/index.php/MacMINLP}
 %
 \item {\tt Meszaros} \url{http://www.doc.ic.ac.uk/~im/00README.QP}
 %
 \item {\tt MINLP} \url{http://www.gamsworld.org/minlp/minlplib.htm}
 %
 \item {\tt POLIP} \url{http://polip.zib.de/pipformat.php}
\end{itemize}
%
Other QP instances were found in libraries devoted to specific optimization problems that can be modeled as QP, such as Max-Cut, the Quadratic Assignment Problem, Portfolio Optimization problems and several others; for reason of space we refrain from listing all these sources.

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\\
\multirow{3}*{Convex}
          & Binary  & Linear    &  2 \\[1.2 ex]
          & \multirow{2}*{Mixed}
                    & Linear    &   13\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
%\hline
\\
\multirow{7}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
          & \multirow{2}*{Mixed}
                    & Linear    &   10\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & Integer & Linear    &    \\
          & \multirow{1}*{Integer}
                    & Linear    &    2\\[1.2 ex]
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\label{tab:FinalSet-D}
\caption{Classification of the final set of discrete instances}
\end{table}

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   11\\[1.2 ex]
                         & Quadratic &   50\\[1.2 ex]
\multirow{3}*{Convex}    
                         & Box       &   3 \\[1.2 ex]
                         & Linear    &   12\\[1.2 ex]
                         & Convex    &    2\\[1.2 ex]
                         & Quadratic &    5\\[1.2 ex]
\multirow{3}*{Quadratic} 
                         & Linear    &   5\\[1.2 ex]
                         & Convex    &   11\\[1.2 ex]
                         & Quadratic &   17\\[1.2 ex]
\hline
Total                    &           & 116 \\
%
\bottomrule
\end{tabular}
\label{tab:FinalSet-C}
\caption{Classification of the final set of continuous instances}
\end{table}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Instance Format}\label{subsec:format}
\framebox{TASK X : write }
In the call for instances no specific formats were imposed
%we did not impose a specific format
for the submissions.
%In this phase we also eliminated multiples copies of the same instance.
To evaluate the instances we decided, for practical reasons, to use Gams as common platform for all the experiments involving commercial solvers.
For this reason, we decided to translate all instances into the \texttt{.gms} Gams format.
 In a preliminary phase, all the instances received were divided according to their format and subsequently translated.
In \S~\ref{subsec:tools}
%~\ref{subsec:CP_convex}
the tools used
to translate an instance from a given format to the \texttt{.gms} format
%to translate an instance from and to a given format to the \texttt{.gms} format
are described in more detail.\\
